---
title: "Fish populations in Bristol Bay, AK"
subtitle: "Proposal"
authors: "Emma Campbell, Gus Compton, Harper Lethin"
format: html
editor: visual
---

```{r load-packages}
#| label: load-pkgs
#| message: false
#| warning: false

library(tidyverse)
```

## Dataset

```{r load-data}
#| label: load-data
#| message: false

## read data 
```

## Reason for Choosing this Dataset

Our goal for this project is XXX. (here we need to put in our high level goal). We chose this data because we think it provides a lot of information across both spatial and temporal scales about fish populations that could reflect some interesting environmental and political variables and that could make for an interesting visualization. We all have pretty environmentally focused interests, so we thought it could be cool to examine an environmental question for this project.

## Questions and Analysis Plan

Our question: How do different fish populations change over time in Bristol Bay in accordance with different policy changes? 

Our plan to answer this question is to merge the different datasets containing information about fish populations, add a variable depicting what policies were in place during the times that each 
