---
title: "Fish populations in Bristol Bay, AK"
subtitle: "Proposal"
authors: "Emma Campbell, Gus Compton, Harper Lethin"
format: html
editor: visual
---

```{r load-packages}
#| label: load-pkgs
#| message: false
#| warning: false

library(tidyverse)
library(readr)
```

## Dataset

```{r load-data}
#| label: load-data
#| message: false

bristolbaydata <- read.csv("salmondata/rawsalmon.csv")
```

## High Level Goal

To create an interactive visualization that allows people to explore how various environmental factors and policy changes affect the salmon population in Bristol Bay.

## Reason for Choosing this Dataset

We chose these data because we think it provides a lot of information across both spatial and temporal scales about salmon populations that could reflect some interesting environmental and political variables and that could make for an interesting visualization. We all have pretty environmentally focused interests, so we thought it could be cool to examine an environmental question for this project.

The variables included in the Alaska Fish Tickets dataset are all quite useful for our analysis. For every year from 1985 to 2023, there are observations for multiple rivers across the Bristol Bay area that include the counts of pounds of landed salmon, their estimated fish counts, and the counts of fishing vessels, processors, and issued permits. This dataset is not tidy, as there are multiple observations for each year, so we'll need to widen it so that one observation is a single year and the different rivers are all columns.

## Questions and Analysis Plan

Our question: How do different fish populations change over time in Bristol Bay in accordance with different policy changes?

Our plan to answer this question is to merge the different datasets containing information about fish populations, add a variable depicting what policies were in place during the times that each population was measured, and then we plan to create an interactive map that shows how the populations changed over time using leaflet that will be organized by different salmon populations and different policies in place.

## Plan of Attack

Week 11:

-   Tidy the dataset (Harper)

-   Identify relevant policy changes around Bristol Bay (Gus)

-   Get environmental data to associate with salmon data (Emma)

-   Draft the code for visualization (Everyone)

Week 12:

-   Get peer reviewed

-   Draft writeup (Harper & Gus)

-   Finalize code (Everyone)

Week 13:

-   Develop presentation (Emma)

-   Present the project

-   Continue working on writeup (Everyone)
